Identification and analysis of pleiotropic expression quantitative trait loci

### 2023-05-05 doc/presentation_230511_centuriday2023/presentation_centuri2023_marseille.tex
DOC presentation

\documentclass{beamer}
\usetheme{Boadilla}

\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{csvsimple}

@@

% Change size of footnotes
\renewcommand{\footnotesize}{\fontsize{5pt}{5pt}\selectfont}
\title{Pleiotropic expression quantitative trait loci are located in cis-regulatory modules, closer to more target genes and with smaller effects on the genes}
\subtitle{Centuri Day 2023}
\author{Aitor Gonz\'alez}
\institute{Aix Marseille Univ, INSERM, TAGC}
\date{May 11, 2023}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \begin{frame}
        \frametitle{Are pleiotropic variants associated to more eQTL genes?}

        \begin{center}
            \includegraphics[width=0.5\textwidth]{\mspath/pltbar_x_per_variant_etissue_y_egene.py/plt.png}
        \end{center}

@@

>>>>

\documentclass{beamer}
\usetheme{Warsaw}
\usecolortheme{seahorse}

\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{csvsimple}
\usepackage{hyperref}

@@

% Change size of footnotes
\renewcommand{\footnotesize}{\fontsize{5pt}{5pt}\selectfont}
\title{Identification and analysis of pleiotropic expression quantitative trait loci}
\subtitle{Centuri Day 2023}
\author{Aitor Gonz\'alez}
\institute{Aix Marseille Univ, INSERM, TAGC}
\date{May 11, 2023}

@@

    \section{Results} %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \begin{frame}
        \frametitle{Is the effect size of pleiotropic eQTLs different?}

        \begin{center}
            \includegraphics[width=0.5\textwidth]{\mspath/plt_x_per_variant_y_egene_distance.py/violin.png}
        \end{center}
        \vfill
        Yes, pleiotropic eQTLs have a lower effect on gene expression and traits

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \begin{frame}
        \frametitle{Are pleiotropic eQTLs closer to genes?}

        \begin{center}
            \includegraphics[width=0.5\textwidth]{\mspath/plt_x_per_variant_y_egene_distance.py/violin.png}
        \end{center}
        \vfill
        Yes, distance to genes decreases with the pleiotropy

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \begin{frame}
        \frametitle{Are pleiotropic eQTLs associated to more genes?}

        \begin{center}
            \includegraphics[width=0.5\textwidth]{\mspath/pltbar_x_per_variant_etissue_y_egene.py/plt.png}
        \end{center}
        \vfill
        Yes, number of target gene increaseas with the pleiotropy

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \begin{frame}
        \frametitle{A web portal to access the eQTL/trait annotations}

        \url{https://gwas2eqtl.tagc.univ-amu.fr/gwas2eqtl}

        \begin{center}
            \includegraphics[width=0.9\textwidth]{fig/gwas2eqtl.png}
        \end{center}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \begin{frame}
        \frametitle{Acknowledgements}

        \begin{itemize}
            \item P Paul
            \item L Lecerf (M1), P Rihet, M Michel, S Marquet, S Spicuglia
        \end{itemize}
%
        \vfill
%
        Funding
%
        \begin{itemize}
            \item Institut Cancer et Immunologie - Aix-Marseille Univ.
            \item Agence nationale de la recherche (ANR)
        \end{itemize}
